LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2022-03-03 src/ms.tex
typo fix, acknowledge our great reviewer

The most fundamental use case of \lw{} is to compute the SNR of an individual binary system. This can be accomplished in \lw{} with only two lines of code - one line to set up the source and another to compute the SNR. As an example one could consider a binary with the parameters
\begin{align*}
    m_1 = m_2 &= 10 \unit{M_{\odot}},\ d = 8 \unit{kpc},\\
    f_{\rm orb} &= 10^{-4} \unit{Hz},\ e = 0.2,
\end{align*}
where $m_1, m_2$ are the primary and secondary masses, $d$ is the distance to the source, $f_{\rm orb}$ is the orbital frequency and $e$ is the eccentricity. As we do not specify a position, polarisation or inclination, \lw{} will calculate the SNR averaged over these quantities. \referee{If a user specifies the position, then if either of the polarisation or inclination are not specified then they will be randomly generated. LEGWORK does not allow users to specify polarisations or inclinations without positions as presume that the user must know the position if they know the polarisation or inclination of the source.} One can now instantiate a source in \lw{} using these parameters (leaving the mission parameters as the default values, such that we compute the SNR for a 4-year LISA mission). As shown in the linked demo, \lw{} quickly computes that the SNR of this binary is $4.49$. In the background, \lw{} decides which SNR approximation is most applicable given the eccentricity of the binary and whether it is stationary in frequency space.

@@

\begin{acknowledgements}
    % People
    We are grateful to Stas Babak, Floor Broekgaarden, Tom Callister, Will Farr, Yi-Ming Hu, Stephen Justham, Valeria Korol, Mike Lau, Tyson Littenberg, Ilya Mandel, Alberto Sesana, Lieke van Son, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project. We thank the BinCosmos group for testing an early version of the package and providing useful feedback. In particular, we thank Lieke van Son for her innovation in inventing the name \lw{}! TW thanks Floor Broekgaarden for first suggesting that he investigate LISA and the derivation of the SNR calculation. KB thanks Shane L. Larson and Kyle Kremer for \emph{several} conversations about the SNR derivation.

>>>>

The most fundamental use case of \lw{} is to compute the SNR of an individual binary system. This can be accomplished in \lw{} with only two lines of code - one line to set up the source and another to compute the SNR. As an example one could consider a binary with the parameters
\begin{align*}
    m_1 = m_2 &= 10 \unit{M_{\odot}},\ d = 8 \unit{kpc},\\
    f_{\rm orb} &= 10^{-4} \unit{Hz},\ e = 0.2,
\end{align*}
where $m_1, m_2$ are the primary and secondary masses, $d$ is the distance to the source, $f_{\rm orb}$ is the orbital frequency and $e$ is the eccentricity. As we do not specify a position, polarisation or inclination, \lw{} will calculate the SNR averaged over these quantities. \referee{If a user specifies the position, then if either of the polarisation or inclination are not specified then they will be randomly generated. LEGWORK does not allow users to specify polarisations or inclinations without positions as we presume that the user must know the position if they know the polarisation or inclination of the source.} One can now instantiate a source in \lw{} using these parameters (leaving the mission parameters as the default values, such that we compute the SNR for a 4-year LISA mission). As shown in the linked demo, \lw{} quickly computes that the SNR of this binary is $4.49$. In the background, \lw{} decides which SNR approximation is most applicable given the eccentricity of the binary and whether it is stationary in frequency space.

@@

\begin{acknowledgements}
    % People
    We are grateful to Stas Babak, Floor Broekgaarden, Tom Callister, Will Farr, Yi-Ming Hu, Stephen Justham, Valeria Korol, Mike Lau, Tyson Littenberg, Ilya Mandel, Alberto Sesana, Lieke van Son, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project. We thank the BinCosmos group for testing an early version of the package and providing useful feedback. In particular, we thank Lieke van Son for her innovation in inventing the name \lw{}! TW thanks Floor Broekgaarden for first suggesting that he investigate LISA and the derivation of the SNR calculation. KB thanks Shane L. Larson and Kyle Kremer for \emph{several} conversations about the SNR derivation. We additionally thank the anonymous reviewer for their useful comments, which helped to improve the quality and clarity of this paper.
